---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warnings = FALSE,
  message=FALSE,
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(devtools)
devtools::install_github("tomambroseharris/THfuncs", force = TRUE)
library(THfuncs)

```


# THfuncs



# Purpose

The THfuncs R packages houses functions created to help with data analysis, data manipulation and other functionality in R. 

The first (and currently only function) contained in this package is `prop_in_group()`. This function transforms tidy data into a grouped proportion table, using columns in the data. It can be generalised to summarise wide data frames, as shown in the example below. 

# Installation

You can install the development version of THfuncs like so:


```{r, echo = TRUE, eval=FALSE}
# install.packages("devtools")
library(devtools)
devtools::install_github("tomambroseharris/THfuncs", force = TRUE)
library(THfuncs)
```



## prop_in_group

See what the function does by running: `?prop_in_group()`

# Example use
```{r, eval=FALSE}
data("iris")
iris
iris <- iris %>% mutate(example_group = if_else(Petal.Length > 4, "long", "short"))

```

The output looks like this

```{r, echo = FALSE, eval = TRUE}
library(magrittr)
library(kableExtra)
library(dplyr)
data("iris")
reformatted_iris <- iris %>% mutate(example_group = if_else(Petal.Length > 4, "long", "short"))

display_iris <- reformatted_iris %>%
  slice_head(n = 5)


display_iris %>% kableExtra::kbl(format = "pipe")
```



```{r, eval=TRUE}
output_table <- prop_in_group(input_df = reformatted_iris,
              value_col = Petal.Length,
              breakdowns_vector = c("Species"),
              group_by_col = example_group,
              knowns_treatment = "count") 



```


```{r}
kableExtra::kbl(output_table, format = "pipe")

```


The proportion of total petal length that is contained in each species is split by the example group: short and long petal lengths, the mutate() assignment for which can be seen above. The breakdowns vector means that multiple different breakdowns can be included in a given table. These will be stacked on top of each other. The text in breakdowns_vector will be parsed to the grouping column, the unique values in that column will become the subgroup. There need be no group_by column. If there is none, the function will operate on the data frame as a whole. 

